Including EW and mixed QCD-EW corrections into PDF fits

### 2020-03-23 paper/paper.tex
some edits in paper
Revert "some edits in paper"
This reverts commit 1325752a4a49f15ce2acfeceb8090e1c2eec6b8b.
Add Marco's changes
Add more text to the PineAPPL section

@@

\section{Technical}

CS, MZ

Describe pineappl, representation of grids, accuracy and performance.\\
We may provide converters from applgrid.\\
How to integrate in MC codes, how this works in aMCblast (setup, MG5 version, urls).\\
Appendix: how to create and fill grids, + simple code.\\

\section{Results}

@@

>>>>

\newcommand{\alphas}{\alpha_{S}}

@@

\section{Binning phase-space weights with \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
\label{sec:pineappl}

\input{pineappl}

\section{Results}
\label{sec:results}

@@

\section{More details about \texorpdfstring{\textsc{PineAPPL}}{PineAPPL}}
\label{app:pineappl-interface}

\input{pineappl-appendix}

### 2020-03-23 paper/pineappl.tex
Add more text to the PineAPPL section

\subsection{PineAPPL}
\label{sec:pineappl}

In this paper we introduce a new program called \textsc{PineAPPL}, which solves the same problem as \textsc{APPLgrid}~\cite{} and \textsc{fastNLO}~\cite{}, but also supports EW corrections, which are the main interest here.
In particular, the following features distinguish it from the two aforementioned programs:
\begin{itemize}
\item support for arbitrary fixed-order calculations in $\alpha$ and $\alpha_\mathrm{s}$ with
\item support for scale variations in multiples of the central renormalization and factorization scale,
\item support for all-order predictions from resummation and photon-/parton-showers,
\item a simple \textsc{C}-interface, with a wrapper for \textsc{Fortran}
\item and support for it implemented in \textsc{mg5\_aMC@NLO},
\item converters to convert \textsc{APPLgrids} and \textsc{fastNLO} tables.
\end{itemize}

@@

\subsection{Grid representation}
\label{sec:grid-representation}

>>>>

In this paper we introduce a new library called \textsc{PineAPPL}, which is similar to \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
Like to those two libraries, also \textsc{PineAPPL} bins phase-space weights in a PDF-independent manner, but it understands EW corrections, which are the main interest in this paper.
The following features distinguish it:
\begin{itemize}
\item Support for arbitrary fixed-order calculations in powers of $\alpha$, $\alpha_\mathrm{s}$ or combinations thereof, e.g.\ in mixed QCD-EW corrections.
Furthermore variations of the renormalization and factorization scale are supported, if needed.
For each needed combination of the couplings and logarithms of renormalization and factorization scale a separate subgrid is created (see Sec.~\ref{sec:grid-representation} for more details);
\item Support for all-order predictions coming from a resummation calculation or a photon-/parton-shower, which are important for some observables (see Sec.~\ref{sec:results}),
\item A simple \textsc{C}-interface, with a wrapper for \textsc{Fortran} and \textsc{Python} (see App.~\ref{app:pineappl-interface} for examples and documentation), which is needed for Monte Carlos and programs to read and write \textsc{PineAPPL} grids.
\textsc{PineAPPL} itself is written in Rust.
\end{itemize}
For \textsc{mg5\_aMC@NLO}~\cite{Alwall:2014hca,Frederix:2018nkq} the interfacing code is already implemented in the most recent version, which replaces the \textsc{aMCfast}~\cite{Bertone:2014zva} interface.
The interfacing code for other Monte Carlo generators should be easy to write, see App.~\ref{app:pineappl-interface} for a small example program.
Finally, \textsc{PineAPPL} provides programs to convert \textsc{APPLgrids} and \textsc{fastNLO} tables to \textsc{PineAPPL} grids.

@@

\subsection{Grid representation and accuracy}
\label{sec:grid-representation}
